\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-26 doc/incertae_sedis.tex
Fix some issues with equations and labels.

In order to determine how the exclude sets should be modified to account for
\emph{incertae sedis} taxa, we first attempt to express the unmodified exclude
sets in a helpful way.  We note that a node $n$ ordinarily excludes the
descendants of $\mathcal{I}(s)$ for all of its siblings, as well as the siblings
of all of its ancestors.  This leads to the following equation:
\begin{eqnarray*}
  \mathcal{E}(n) & = \mathcal{L} - \mathcal{I}(n)\\
 & =\left[\mathcal{I}(s)\big|a\in n+ancestors(n),s\in siblings(a)\right]\\
 & =\left[\mathcal{I}(s)\big|s\in siblings(n)\right]\cup\left[\mathcal{I}(s)\big|a\in ancestors(n),s\in siblings(a)\right]\\
 & =\left[\mathcal{I}(s)\big|s\in siblings(n)\right]\cup\mathcal{E}(parent(n)) \label{eq:exsetformtraditional}
\end{eqnarray*}

When modifying the exclude set for a node $n$, we seek to find all the \emph{incertae
sedis} taxa that may intrude into it. It turns out that the incertae sedis taxa that
might intrude are just the \emph{incertae sedis} siblings of $n$ and all of its ancestors.
\begin{align*}
\mathcal{E}(n) & =
    \left[\mathcal{I}(s)\big|a\in n+ancestors(n),s\in siblings(a),s\text{ not \emph{incertae sedis}}\right]\\
& =\left[\mathcal{I}(s)\big|s\in siblings(n),s\text{ not \emph{incertae sedis}}\right]\cup\\
& \,\,\,\,\,\,\,\,\,\,\,\,\left[\mathcal{I}(s)\big|a\in ancestors(n),s\in siblings(a),s\text{ not \emph{incertae sedis}}\right]\\
& =\left[\mathcal{I}(s)\big|s\in siblings(n),s\text{ not \emph{incertae sedis}}\right]\cup\mathcal{E}(parent(n)).
\label{eq:exsetformonea}
\end{align*}
This formula allows us to compute exclude sets via a pre-order traversal on the
taxonomy tree with the exclude set for the root node defined to be $\emptyset$.

>>>>

In order to determine how the exclude sets should be modified to account for
\emph{incertae sedis} taxa, we first attempt to express the unmodified exclude
sets in a helpful way.  We note that a node $n$ ordinarily excludes the
descendants of $\mathcal{I}(s)$ for all of its siblings, as well as the siblings
of all of its ancestors.  This leads to the following equation:
\begin{align}
\mathcal{E}(n) & = \mathcal{L} - \mathcal{I}(n)\nonumber\\
 & =\left[\mathcal{I}(s)\big|a\in n+ancestors(n),s\in siblings(a)\right]\nonumber\\
 & =\left[\mathcal{I}(s)\big|s\in siblings(n)\right]\cup\left[\mathcal{I}(s)\big|a\in ancestors(n),s\in siblings(a)\right]\nonumber\\
 & =\left[\mathcal{I}(s)\big|s\in siblings(n)\right]\cup\mathcal{E}(parent(n)).\label{eq:exsetformonea-traditional}
\end{align}

When modifying the exclude set for a node $n$, we seek to find all the \emph{incertae
sedis} taxa that may intrude into it. It turns out that the incertae sedis taxa that
might intrude are just the \emph{incertae sedis} siblings of $n$ and all of its ancestors.
\begin{align}
\mathcal{E}(n) & =
    \left[\mathcal{I}(s)\big|a\in n+ancestors(n),s\in siblings(a),s\text{ not \emph{incertae sedis}}\right]\nonumber\\
& =\left[\mathcal{I}(s)\big|s\in siblings(n),s\text{ not \emph{incertae sedis}}\right]\cup\nonumber\\
& \,\,\,\,\,\,\,\,\,\,\,\,\left[\mathcal{I}(s)\big|a\in ancestors(n),s\in siblings(a),s\text{ not \emph{incertae sedis}}\right]\nonumber\\
& =\left[\mathcal{I}(s)\big|s\in siblings(n),s\text{ not \emph{incertae sedis}}\right]\cup\mathcal{E}(parent(n)).\label{eq:exsetformonea}
\end{align}
This formula allows us to compute exclude sets via a pre-order traversal on the
taxonomy tree with the exclude set for the root node defined to be $\emptyset$.
